A Reproducible Workflow with RMarkdown, Git, Make & Docker

### 2019-08-20 rr-flow.Rmd
resolve #6

This folder, where everything resides that you need for analysis, is referred to as a Projekt. Working with Projects is exceptionally comfortable with RStudio an integrated development environment (IDE) for R.

>>>>

This folder, where everything resides that you need for analysis (code & data), is referred to as a Projekt. Working with Projects is exceptionally comfortable with RStudio an integrated development environment (IDE) for R. It is usefull to organize this Project in way that strictly segregates (raw) data and code by placing them in directories called `data` and `R` [see Section 4 @marwickPackagingDataAnalytical2018].
